Revision 2: Responses to Reviewers Round 2

### 2018-10-09 jfs_submission/paper-pre-submission-revision-2/Responses-round2.Rmd
after submission revision 2- note: the manuscript file has been rewritted, its a different file from the previous commit

We would like to thank the reviewers for their in-depth reviews and the suggestions regarding the manuscript. Please find our detailed response addressing each of the points below.

@@

*We have changed the sentence to: This data forms the basis of a statistical analysis that allow us to quantify similarity of markings and serves as a basis for error rate calculations*

@@

*We now have changed all reported numbers regarding errors to percentages, including all figures.*

@@

*We have softened the sentence at the end of the paragraph. We also did not mean to make this sentence an absolute statement but were rather speculating ourselves. We have made the change to the manuscript to reflect that better.*

>>>>

We would again like to thank the reviewers for their in-depth reviews and the suggestions regarding the manuscript. Please find our detailed response addressing each of the points below.

@@

*Thank you for the comment. We have changed the sentence to: This data forms the basis of a statistical analysis that allow us to quantify similarity of markings and serves as a basis for error rate calculations*

@@

*Thank you for poining this out. We now have changed all reported numbers regarding errors to percentages, including all figures.*

@@

*Thank you for the comment. We have softened the sentence at the end of the paragraph. We also did not mean to make this sentence an absolute statement but were rather speculating ourselves. We have made the change to the manuscript to reflect that better.*
